R Notebook

### 2021-09-14 documentation_and_analysis/draftbook.Rmd
Created heatmap of NO2 across UK

```{r}
library(tidyverse)
library(janitor)
library(readODS)
library(httr)
library(here)
library(data.table)
library(sf)
library(leaflet)
```

@@

```{r}
air_pollution <- GET("https://uk-air.defra.gov.uk/data/sos/service?service=AQD&version=1.0.0&request=GetObservation&temporalFilter=om:phenomenonTime,After,yyyy-mm-ddT00:00:00.000Z") 
```

```{r}
air_pollution <- rbindlist(air_pollution$content, fill = TRUE) 
```

@@

>>>>

```{r}
library(tidyverse)
library(janitor)
library(readODS)
library(httr)
library(here)
library(data.table)
library(sf)
library(leaflet)
library(leaflet.extras)
```

@@

```{r}
air_pollution_cap <- GET("https://uk-air.defra.gov.uk/data/sos/service?service=AQD&request=GetCapabilities")
```

```{r}
air_pollution_cap <- rbindlist(air_pollution$content, fill = TRUE)
```

```{r}
air_pollution_cap <- unnest(air_pollution_cap)
```

```{r}
air_pollution <- GET("https://uk-air.defra.gov.uk/data/sos/service?service=SOS&version=2.0.0&request=GetObserved&observedProperty=http://dd.eionet.europa.eu/vocabulary/aq/pollutant/8") %>% 
  content()
```

```{r}
air_pollution$exceptions
```

```{r}
air_pollution <- rbindlist(air_pollution$exceptions, fill = TRUE) 
```

@@

```{r}
# Remove missing NO2 grid values
no2_clean <- no2_all %>% 
  filter(no2 != "MISSING")
```

```{r}
library(proj4)
proj4string <- "+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs"

no2_clean_row <- no2_clean %>% 
  rowid_to_column()

# Source data
xy <- no2_clean_row %>% 
  select(x, y, rowid)

# Transformed data
pj <- project(xy, proj4string, inverse=TRUE)
latlon <- data.frame(xy, lat=pj$y, lon=pj$x)
final <-  merge(no2_clean_row, latlon, by.x = "rowid", by.y = "rowid") %>%
  filter(year == 2019) %>% 
  select(lat, lon, no2)

```

```{r}
leaflet() %>%
  addProviderTiles("CartoDB.Positron", options = providerTileOptions(noWrap = TRUE)) %>%
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addHeatmap(data = final,
             lng = ~lon, 
             lat = ~lat, 
             intensity = ~no2,
             minOpacity = 0.05,
             max = 5,
             radius = 7)
```
